Distributed Decision Making for Dynamic Formation of Web Services Communities

### 2015-01-14 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

  \item \emph{Throughput $(Th_{C})$} is the rate at which a service can process requests. QoS measures can include the maximum throughput or a function that describes how throughput varies with load intensity. Throughput is a positive real number. For communities the expected throughput value of collaborating web services can be estimated as:

@@

	\item \emph{Execution Time $(Et_{C})$} is the time a service takes to respond to various types of requests. 
	%is the expected delay between the time instant when a request is sent and the time when the result is obtained. 
	Execution time is measured in milliseconds. Execution time can be affected by load intensity, which can be measured in terms of arrival rates (such as requests per second) or number of concurrent requests. This internal feature is a positive integer. For communities, the expected execution time of collaborating web services can be estimated as:

@@

In order to evaluate the performance of the mechanism, we used \emph{Receiver Operating Characteristic (ROC) curve}, which is a graphical plot illustrating the true negative rate against the false positive rate at various threshold settings in classifier systems. In order to classify our communities' selection strategies correctly, for each community, we evaluated the training process by replacing the community in the set with the closest one, from which it gets the strategy profile. If the actions are the same and the same utility levels are gained, we classify the decision as correct. Otherwise, it is classified as a wrong decision. \emph{AUC}, the area under the \emph{ROC curve}, is equal to the probability that a classifier will rank a randomly chosen positive instance higher than a randomly chosen negative one, and the higher number reflects better performance from the better solution.  Figure \ref{roc5} illustrates the \emph{ROC curve} evaluation of the DDM decision making mechanism. We compare our method with two other methods. The \emph{rational} method is based on the assumption that communities, as rational agents, join a community that increases their utility. The \emph{greedy} method only looks up the available list of communities and simply joins the community that maximizes its utility without considering any long-term strategy or  other communities' acceptance scenarios. Figure \ref{roc5} compares the results for all methods. The two other methods have very high failure rates compared to our method. Table \ref{fail_rate} illustrates the number of communities that failed to find the optimal collaboration group. The results support the need for a long-term training model in a successful decision making process.

>>>>

  \item \emph{Throughput $(Th_{C})$} is the rate at which a service can process requests. QoS measures can include the maximum throughput or a function that describes how throughput varies with load intensity. Throughput is a positive real number. For communities the expected throughput value of collaborating web services can be estimated as summation of throughputs of all the services inside:

@@

	\item \emph{Execution Time $(Et_{C})$} is the time a service takes to respond to various types of requests. 
	%is the expected delay between the time instant when a request is sent and the time when the result is obtained. 
	Execution time is measured in milliseconds. Execution time can be affected by load intensity, which can be measured in terms of arrival rates (such as requests per second) or number of concurrent requests. This internal feature is a positive integer. For communities, the expected execution time of collaborating web services can be estimated as the execution time of the bottleneck service which is the service with the slowest execution time:

@@

In order to evaluate the performance of the mechanism, we used \emph{Receiver Operating Characteristic (ROC) curve}, which is a graphical plot illustrating the true negative rate against the false positive rate at various threshold settings in classifier systems. In order to classify our communities' selection strategies correctly, for each community, we evaluated the training process by replacing the community in the set with the closest one, from which it gets the strategy profile. If the actions are the same and the same utility levels are gained, we classify the decision as correct. Otherwise, it is classified as a wrong decision. \emph{AUC}, the area under the \emph{ROC curve}, is equal to the probability that a classifier will rank a randomly chosen positive instance higher than a randomly chosen negative one, and the higher number reflects better performance from the better solution.  Figure \ref{roc5} illustrates the \emph{ROC curve} evaluation of the DDM decision making mechanism. We compare our method with two other methods. The \emph{rational} method is based on the assumption that communities, as rational agents, join a community that increases their utility. The \emph{greedy} method only looks up the available list of communities and simply joins the community that maximizes its utility without considering any long-term strategy or other communities' acceptance scenarios, its an greedy algorithm and chooses a locally optimal choice. Therefore we use these two methods as our benchmark:

\begin{itemize}
  \item {\bf Rational Method:} Communities would send a join request to any available community, which will increase the utility. The other community would accept the join offer if the utility gain is positive as well.
	\item {\bf Greedy Method:} Communities do a linear search among all the available communities and send a join request to the community which results in maximum utility, The other community would accept the join offer if the utility gain is positive and the utility gain does not need to be the maximum for the community recieving the join request.
\end{itemize}

Figure \ref{roc5} compares the results for all methods. The two other methods have very high failure rates compared to our method. Table \ref{fail_rate} illustrates the number of communities that failed to find the optimal collaboration group. The results support the need for a long-term training model in a successful decision making process.
